Modeling vertical-axis cross-flow turbine wakes

### 2015-08-12 paper.tex
Start conclusions

>>>>

\section{Conclusions}

A cross-flow turbine was modeled using the $k$--$\omega$ SST and
Spalart--Allmaras Reynolds-averaged Navier--Stokes turbulence models to test
their abilities to predict turbine performance and near-wake dynamics. It was
observed that when modeled in 2-D, the performance is over-predicted compared to
the data from the tow tank experiments, which was expected due to omission of
blade end effects, support strut drag, and increased blockage. Vertical (or
axial) wake dynamics were unresolved in the 2-D model, despite being identified
as a significant contributor to streamwise wake recovery, which casts doubt on
the 2-D model's applicability as a tool to study array spacing effects.
